---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# luar

[![Coverage status](https://codecov.io/gh/noamross/luar/branch/master/graph/badge.svg)](https://codecov.io/github/noamross/luar?branch=master)
[![Coverage status](https://codecov.io/gh/noamross/luar/branch/master/graph/badge.svg)](https://codecov.io/github/noamross/luar?branch=master)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

The goal of luar is to explore embedding of the [lua language](https://www.lua.org) in R.  It's mostly an experiment for me to understand wrapping C libraries.

## Installation

You can install luar from GitHub with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("noamross/luar")
```

_Should_ you install luar? I dunno.

---

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By participating in this project you agree to abide by its terms.
